%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%
{This Master thesis is an extensive research of my Master study in Communications
Engineering at Technical University of Munich, Germany, from March
2019 to September 2019. My thesis had been mainly conducted at Antonia
Wachter-Zeh's group Coding for Communications and Data Storage. During
my thesis writing period, many people supported and motivated me,
and I am profoundly thankful to all of them.

First of all, I would like to thank Sven Puchinger for being a devoted
supervisor. Sven inspired me with his plenty of ideas during any of
our weekly discussion and motivated me to solve new research problems.
I really appreciate that Sven comprehensively reviewed my thesis writing
for multiple rounds to have the current version. I would also like
to thank Sven for supporting me to get access to the student laboratory
to prepare my thesis literature review and the whole time of my thesis. 

Secondly, Antonia gave me first lectures in Coding Theory and motivated
me to write my thesis in Network Coding. Her advice along my thesis
is definitely valuable on paving my future career as an young engineer.

Thirdly, thanks to my flatmate Taylor Johnson, my thesis includes
various sentence structure. Two of my classmates Karthik Uppund and
Shinho Choe have made a great support from my start of the thesis.
I would like to thank Shinho for awesome discussion on probabilistic
problems during lunch breaks, and Karthik for his time to proofread
my thesis writing before my final presentation.

Finally, I would like to thank my family, in particular my my mother
Kim and my brother Hai, who have always supported and encouraged me
through my entire life. I am also definitely grateful to my soulmate
Trang for always loving and supporting me.

~

~

~

Munich, September 2019

Ha Nguyen
}
